Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-21 revision_plan.tex
E3

>>>>

{\it \paragraph{E.3: Reviewer Comment:} Fairness and TCP friendliness discussion are missing: tail FCT of large flows can tell the impact on fairness but is completely missing.}

\noindent\textcolor{blue}{\textbf{Response E.2}
PPT's HCP is exactly DCTCP. So, PPT can coexist with the TCP family of transports friendly.
To be frank, we have not taken into account the fairness issue.
We will discuss this point in Appendix A.
}
